Comparing assessment results with truth: first pass

### 2019-10-02 SkillAssessInit.Rmd
add initial comparisons

```{r}
library(here)
library(r4ss)
library(atlantisom)
library(dplyr)
library(ggplot2)
```

@@

Reading in the truth--these files were generated and saved previously [here](https://sgaichas.github.io/poseidon-dev/SardinesHakeatlantisom2SStest.html).

@@

@@

@@

@@

```{r compare R}

>>>>

```{r}
library(here)
library(r4ss)
library(atlantisom)
library(dplyr)
library(ggplot2)
library(ggthemes)
```

@@

Reading in the truth--these files were generated and saved previously [here](https://sgaichas.github.io/poseidon-dev/SardinesHakeatlantisom2SStest.html). Recruitment and mortality are detailed [here](https://sgaichas.github.io/poseidon-dev/TestCalcZ2.html).

@@

#Load functional groups
funct.groups <- load_fgs(dir=d.name,
                         file_fgs = functional.groups.file)
#Get just the names of active functional groups
funct.group.names <- funct.groups %>% 
  filter(IsTurnedOn == 1) %>%
  select(Name) %>%
  .$Name

@@

YOY <- atlantisom::load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

# load biolprm in some initialize file?
biol <- atlantisom::load_biolprm(d.name, biol.prm.file)

# get code matching species name to split YOY file
code_ss <- funct.groups$Code[which(funct.groups$Name == species_ss)]

# cut to a single species in YOY file
YOY_ss <- YOY %>%
  select(Time, paste0(code_ss, ".0"))

# mg carbon converted to wet weight in tonnes
k_wetdry <- biol$kgw2d / 1000000000

# WARNING only works for CCA because YOY.txt rows 2:end are already in numbers
# and we are merging out the incorrect and irrelevant YOY row 1 (Time=0)
# also hardcoded for sardine example
recnums <- YOY_ss %>%
  mutate(yr = as.integer(round(YOY_ss$Time)/365)) %>%
  mutate(recnums = SAR.0/k_wetdry/biol$redfieldcn) %>%
  filter(yr>0)

file.mort <- file.path(d.name, paste0("output", scenario.name, "Mort.txt"))

mortish <- read.table(file.mort, header = TRUE)

relF_ss <- mortish %>%
  select(Time, relF = paste0(code_ss, ".F"))

@@

names(replist$timeseries)[19]<-"Fmort"

@@

```{r compareR}

plotR <-ggplot() +
  geom_line(data=recnums, aes(x=yr,y=recnums, color="True R"), 
            alpha = 10/10) +
  geom_point(data=replist$timeseries, aes(x=Yr,y=(Recruit_0*1000), color="SS3 Est R"),
             alpha = 10/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotR

```
And F (understanding that F in the mort.txt file from Atlantis is relative, just looking for patterns).

```{r compare-F}

plotF <-ggplot() +
  geom_line(data=relF_ss, aes(x=Time/365, y=relF, color="True F"), 
            alpha = 10/10) +
  geom_point(data=replist$timeseries, aes(x=Yr,y=Fmort, color="SS3 Est F"),
             alpha = 10/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotF
